Rclean: A Tool for Writing Cleaner, More Transparent Code

### 2020-02-04 joss/paper.Rmd
Removes library and data package discussion

To conclude, we hope that `Rclean` makes writing scientific software
easier. We look forward to feedback and help with extending its
applications, particularly in the area of reproducibility, such as
using code cleaning in the creation of more robust capsules
[@Pasquier2018]. To get involved, report bugs, suggest features,
please visit the project page.

>>>>

To conclude, we hope that `Rclean` makes writing scientific software
easier for the R community. We look forward to feedback and help with
extending its application, particularly in the area of
reproducibility, such as using code cleaning in the creation of more
robust capsules [@Pasquier2018]. To get involved, report bugs, suggest
features, please visit the project page.
